Carbonate chemistry at Ny-Ålesund

### 2023-03-13 awipev-CO2.Rmd
Fig. time series finalized

ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb_mix), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="A",x="", y="Salinity") +
  Mytheme(size_labs = size_labs) +
  theme(axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold")
        )

# temp_insitu_11m
ts_temp <- d_all %>%
  ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="B",x="", y="Temperature (°C)") +
  Mytheme(size_labs = size_labs) +
  theme(axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold")
        )
# PAR
ts_par_air <- d_all %>%
  ggplot(aes(x = datetime, y = par_air), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="Atmospheric PAR",x="", 
       y=latex2exp::TeX("PAR ($\\mu mol\\phantom{x}m^{-2}\\phantom{x}s^{-1})$")) +
  Mytheme(size_labs = size_labs) +
  theme(axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs))

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_fb_insi_temp), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  geom_point(aes(x = datetime, y = pco2_calc_fb_insi_temp), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="C",
       subtitle = NULL,
       x="", y=latex2exp::TeX("pCO$_2$ ($\\mu atm$)", bold=TRUE)) +
  Mytheme(size_labs = size_labs) +
  theme(axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold")
        )
# SEAFET pH
ts_pH <- d_all %>% 
  dplyr::filter(depth > 8) %>% 
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pHint_tot_sf), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="D", 
       subtitle =NULL,
       x = "", y=latex2exp::TeX("pH$_T$", bold=TRUE)) +
  Mytheme(size_labs = size_labs) +
  theme(legend.position = c(0.1, 0.5),
        legend.key.height = unit(0.5, 'cm')) +
  theme(axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold")
        )
# AT
ts_at <- d_all %>%
  ggplot(aes(x = datetime, y = at_calc), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="E", 
       subtitle = NULL,
       x="", y=latex2exp::TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$", bold = TRUE)) +
  Mytheme(size_labs = size_labs) +
  theme(axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold")
        )

@@

# identify extremes
d_bp <- d_bp %>%
    ext_sal_fb_mix = ifelse(
      sal_fb_mix < dec_sal_fb_mix[1] |
        sal_fb_mix > dec_sal_fb_mix[2],
      sal_fb_mix,
      NA
    ),
    ext_temp_insitu_11m = ifelse(
      temp_insitu_11m < dec_temp_insitu_11m[1] |
        temp_insitu_11m > dec_temp_insitu_11m[2],
      temp_insitu_11m,
      NA
    ),
    ext_pco2_fb = ifelse(pco2_fb < dec_pco2_fb[1] |
                           pco2_fb > dec_pco2_fb[2], pco2_fb, NA),
    ext_pHint_tot_sf = ifelse(
      pHint_tot_sf < dec_pHint_tot_sf[1] |
        pHint_tot_sf > dec_pHint_tot_sf[2],
      pHint_tot_sf,
      NA
    ),
    ext_at_calc = ifelse(at_calc < dec_at_calc[1] |
                           at_calc > dec_at_calc[2], at_calc, NA)
ts_sal_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="F", y = "Salinity", x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
#        aspect.ratio=0.5,
        axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold")
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_temp_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="G", y = "Temperature (°C)", x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
#        aspect.ratio=0.5,
        axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold")
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_pco2_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="H", y = latex2exp::TeX("pCO$_2$ ($\\mu atm$)", bold = TRUE), x=NULL) +
  Mytheme(size_labs = size_labs)+
  theme(panel.grid.major.x = element_blank(),
#        aspect.ratio=0.5,
        axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold")
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_pH_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="I", y = latex2exp::TeX("$pH_T$", bold = TRUE), x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
#        aspect.ratio=0.5,
        axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold")
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_at_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="J", y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$", bold = TRUE), x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
#        aspect.ratio=0.5,
        axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold")
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
# Combine plots
g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
g2 <- g2 + plot_annotation(tag_levels = 'A') & 
                             theme(plot.tag = element_text(face = "bold"))
ggsave(filename = "figures/ts_boxplots.png", plot = g2, width = 12)

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at) |
  (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
#g <- g + patchwork::plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold", size = 14))
ggsave(filename = "figures/essd/ts.pdf", plot = g, width = 12)
# legend:
# - Salinity below 8m
# - In situ temperature (11m)
# - pCO2 at 11 m and insitu Temperature, measued in blue, calculated from CT an AT in red
# - In situ pH below 8 m at in situ Temperature, seaFET in blue, spectrophotometric in red
# - Total alkalinity calculated from salinity in blue, discrete measurement in red

>>>>

ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb_mix), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="A",x=NULL, y="Salinity") +
  scale_y_continuous(limits = c(31.8, 35.5)) +
  Mytheme(size_labs = size_labs) +
  theme(#axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        axis.text.x=element_blank(),
        title = element_text(colour="black", size=14, face="bold"),
         axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        )

# temp_insitu_11m
ts_temp <- d_all %>%
  ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="B",x=NULL, y="Temperature (°C)") +
  scale_y_continuous(limits = c(-1.8, 8)) +
  Mytheme(size_labs = size_labs) +
  theme(#axis.title.x = element_text(face = "bold", size = size_labs),
        axis.text.x=element_blank(),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        )
# PAR
ts_par_air <- d_all %>%
  ggplot(aes(x = datetime, y = par_air), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="Atmospheric PAR",x="", 
       y=latex2exp::TeX("PAR ($\\mu mol\\phantom{x}m^{-2}\\phantom{x}s^{-1})$")) +
  Mytheme(size_labs = size_labs) +
  theme(axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs))

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_fb_insi_temp), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  geom_point(aes(x = datetime, y = pco2_calc_fb_insi_temp), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="C",
       subtitle = NULL,
       x=NULL, y=latex2exp::TeX("pCO$_2$ ($\\mu atm$)", bold=TRUE)) +
  scale_y_continuous(limits = c(180, 400)) +
  Mytheme(size_labs = size_labs) +
  theme(#axis.title.x = element_text(face = "bold", size = size_labs),
        axis.text.x=element_blank(),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        )
# SEAFET pH
ts_pH <- d_all %>% 
  dplyr::filter(depth > 8) %>% 
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pHint_tot_sf), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="D", 
       subtitle =NULL,
       x = NULL, y=latex2exp::TeX("pH$_T$", bold=TRUE)) +
  scale_y_continuous(limits = c(7.99, 8.2)) +
  Mytheme(size_labs = size_labs) +
  theme(legend.position = c(0.1, 0.5),
        legend.key.height = unit(0.5, 'cm')) +
  theme(#axis.title.x = element_text(face = "bold", size = size_labs),
        axis.text.x=element_blank(),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        )
# AT
ts_at <- d_all %>%
  ggplot(aes(x = datetime, y = at_calc), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="E", 
       subtitle = NULL,
       x="Year", y=latex2exp::TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$", bold = TRUE)) +
  scale_y_continuous(limits = c(2135, 2355)) +
  Mytheme(size_labs = size_labs) +
  theme(axis.title.x = element_text(face = "bold", size = size_labs),
        #axis.text.x=element_blank(),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        )

@@

# identify extremes
d_bp <- d_bp %>%
  dplyr::mutate(
    ext_sal_fb_mix = ifelse(
      sal_fb_mix < dec_sal_fb_mix[1] |
        sal_fb_mix > dec_sal_fb_mix[2],
      sal_fb_mix,
      NA
    ),
    ext_temp_insitu_11m = ifelse(
      temp_insitu_11m < dec_temp_insitu_11m[1] |
        temp_insitu_11m > dec_temp_insitu_11m[2],
      temp_insitu_11m,
      NA
    ),
    ext_pco2_fb = ifelse(pco2_fb < dec_pco2_fb[1] |
                           pco2_fb > dec_pco2_fb[2], pco2_fb, NA),
    ext_pHint_tot_sf = ifelse(
      pHint_tot_sf < dec_pHint_tot_sf[1] |
        pHint_tot_sf > dec_pHint_tot_sf[2],
      pHint_tot_sf,
      NA
    ),
    ext_at_calc = ifelse(at_calc < dec_at_calc[1] |
                           at_calc > dec_at_calc[2], at_calc, NA)
  )
ts_sal_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="F", y = NULL, x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  # scale_y_continuous(limits = c(31.8, 35.5))

ts_temp_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="G", y = NULL, x=NULL) +
  scale_y_continuous(limits = c(-1.8, 8)) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))

ts_pco2_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="H", y = NULL, x=NULL) +
  scale_y_continuous(limits = c(180, 400)) +
  Mytheme(size_labs = size_labs)+
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_pH_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="I", y = NULL, x=NULL) +
  scale_y_continuous(limits = c(7.99, 8.2)) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))

ts_at_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="J", y = NULL, x="Month") +
  scale_y_continuous(limits = c(2135, 2355)) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        #axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.title.x = element_text(face = "bold", size = size_labs),
        #axis.label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
# Combine plots
g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
g2 <- g2 + plot_annotation(tag_levels = 'A') & 
                             theme(plot.tag = element_text(face = "bold"))
ggsave(filename = "figures/ts_boxplots.png", plot = g2, width = 12)
```

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
#g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at) |
#  (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
g <- (ts_sal | ts_sal_bp) / (ts_temp | ts_temp_bp) / (ts_pCO2 | ts_pco2_bp) / 
  (ts_pH | ts_pH_bp) / (ts_at | ts_at_bp)
#g <- g + patchwork::plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold", size = 14))
ggsave(filename = "figures/essd/ts.pdf", plot = g, width = 8)
# legend:
# - Salinity below 8m
# - In situ temperature (11m)
# - pCO2 at 11 m and insitu Temperature, measued in blue, calculated from CT an AT in red
# - In situ pH below 8 m at in situ Temperature, seaFET in blue, spectrophotometric in red
# - Total alkalinity calculated from salinity in blue, discrete measurement in red
